manuscript

### 2023-11-26 scripts/manuscript.qmd
Added a few comments and one small change to labs

```{r}
#| include: FALSE
library(tidyverse)
library(here)
library(rio)
library(psych)
library(janitor)
library(ggplot2)
```

@@

ggplot(communication, aes(gender, ppis_1_score, fill=gender)) +
  geom_boxplot() +
  theme(legend.position = "none") +
    scale_x_discrete(limits = c("Female", "Male", "Non-binary")) +
  labs(x = "Gender",
       y = "Teacher Invasive Behaviors Score",
       title = "Boxplot of Teacher Invasive Behaviors Score by Gender")

@@

>>>>

```{r}
#| include: FALSE
library(tidyverse)
library(here)
library(rio)
library(psych)
library(janitor)
library(ggplot2)

#comment from Frances: I'm not familiar with the psych package - where are you using it?
```

@@

ggplot(communication, aes(gender, ppis_1_score, fill=gender)) +
  geom_boxplot() +
  theme(legend.position = "none") +
    scale_x_discrete(limits = c("Female", "Male", "Non-binary")) +
  labs(x = "Gender",
       y = "Teacher Invasive Behaviors Score",
       title = "Boxplot of Teacher Invasive Behaviors Score by Gender",
       subtitle = "Sampled from undergraduate student population in Minnesota, (year?)")

#added a subtitle to indicate age, location, and year of participant survey

@@

#comment from Frances: I like these boxplots - the data is super clear! You may consider adding a subtitle with a little more information about the study (age, year data was collected, etc.)
